Multi-scale assessment of a grassland productivity model

### 2020-12-27 manuscript/manuscript.Rmd
eq corrections, add note for new supp

The PhenoGrass model is an ecohydrology model which has interacting state variables for soil water, plant available water, and plant fractional cover [@hufkens2016]. Model inputs are daily precipitation, temperature, potential evapotranspiration (derived from the Hargreaves equation, @hargreaves1985), and solar radiation. The primary output is fractional vegetation cover (fCover). The original model form, derived in Choler et 2010 and Choler et al. 2011, used only temperature and potential evapotranspiration and was parameterized using satellite-derived NDVI data. @hufkens2016 expanded on the original Choler model by incorporating growth and senescence restraints from temperature and solar radiation, and also included a scaling factor to convert PhenoCam G\textsubscript{cc} data to a fractional cover estimate. @hufkens2016 evaluated the PhenoGrass model using 14 grassland PhenoCam sites across Western North America with a total of 34 site years. They found the modelled fractional cover correlated well with annual productivity at both a daily and annual timescale. Despite it's name the PhenoGrass model can theoretically apply to any vegetation type with a distinct growth signal in response to precipitation, as hypothesized in the original threshold-delay model [@ogle2004]. Here we use two additional vegetation types, shrubs and agricultural plots, to test how applicable it is beyond grasslands.

@@

\begin{equation}
CVMAE_{j} = \frac{\frac{1}{i}\sum_{i=1}^{n}|fCover_{i,obs} - fCover_{i,pred}|}{\overline{fCover_{obs}}}
\end{equation}

where \textit{N} is the number of sites within the spatial scale evaluated and \textit{n} is the number of daily values at each site, \textit{fCover\textsubscript{i,obs}} and \textit{fCover\textsubscript{i,pred}} are observed and predicted values, respectively. \textit{fCover\textsubscript{pred}} is the average observed \textit{fCover} at each site.

>>>>

The PhenoGrass model is an ecohydrology model which has interacting state variables for soil water, plant available water, and plant fractional cover [@hufkens2016]. Model inputs are daily precipitation, temperature, potential evapotranspiration (derived from the Hargreaves equation, @hargreaves1985), and solar radiation. The primary output is fractional vegetation cover (fCover). The original model form, derived in Choler et 2010 and Choler et al. 2011, used only temperature and potential evapotranspiration and was parameterized using satellite-derived NDVI data. @hufkens2016 expanded on the original Choler model by incorporating growth and senescence restraints from temperature and solar radiation, and also included a scaling factor to convert PhenoCam G\textsubscript{cc} data to a fractional cover estimate (see supplemental equations). @hufkens2016 evaluated the PhenoGrass model using 14 grassland PhenoCam sites across Western North America with a total of 34 site years. They found the modelled fractional cover correlated well with annual productivity at both a daily and annual timescale. Despite it's name the PhenoGrass model can theoretically apply to any vegetation type with a distinct growth signal in response to precipitation, as hypothesized in the original threshold-delay model [@ogle2004]. Here we use two additional vegetation types, shrubs and agricultural plots, to test how applicable it is beyond grasslands.

@@

\begin{equation}
CVMAE_{j} = \frac{\frac{1}{n}\sum_{i=1}^{n}|fCover_{i,obs} - fCover_{i,pred}|}{\overline{fCover_{obs}}}
\end{equation}

where \textit{N} is the number of sites within the spatial scale evaluated and \textit{n} is the number of daily values at each site, \textit{fCover\textsubscript{i,obs}} and \textit{fCover\textsubscript{i,pred}} are observed and predicted values, respectively. \(\overline{fCover_{obs}}\) is the average observed \textit{fCover} at each site.
